---
title: "Vignette for Linear Regression"
author: "Farha Shazmeen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
In statistics the most widely used techniques is linear regression where we study the potential relationship between the variables. The relation between **independent variable** and **dependent variable**(often called response variables). For fitting a range of linear models to find the complex relationships between the variables.


The simple way to calculate the statistics of data in a  different way  is to use **ordinary linear algebra** and calculate the following:


- Regressions coefficients
- The Fitted values
- The residuals
- The degrees of freedom
- The residual variance
- The p-vales and t-values


## Vignette Info

Vignette for the package 4 is written. The Linear Regression class is to be build with the use of reference class. You can  use **setRefClass**. It has following methods:

- **new** for creating new objects of that class. 

- Methods for modifying existing or adding new methods

- Fields to get a list of fields defined for class




## Examples

Here the linear regression is performed between the indepedent variable **Petal.Width** and dependent variable **Speices**. <br /> <br />
The **coefficients** for  Linear Regression are:
 $Y = X\beta + \epsilon$

```{r}
a<-lm(Petal.Width ~ Species, data=iris)
a$coefficients
```
<br />

The **Summary** of the the coefficients with their standard error, t-value and p-value as well as the estimate of sigma and the degrees
of freedom for the model.

```{r}
summary(lm(Petal.Length ~ Species, data=iris))
```
</br >
The **Fitted** values are

```{r}
fitted(a)
```
</br>

The **Residual** values are 
```{r}
residuals(a)
```


## Figures
Diagnostic plots:

</br >


```{r fig1, fig.height = 4, fig.width = 6}
plot(a)
```






